---
title: "WorldUniversityRankings"
author: "Yasko"
date: "2022-10-21"
output:
  html_document:
    toc: yes
    df_print: paged
    theme: united
---
## World University Rankings

```{r Libraries, message=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(formattable)
library(dplyr)
library(tm)
library(tidyr)
library(wordcloud)
library(ggplot2)
library(gridExtra)
library(grid)
library(plotly)
library(corrplot)
library(ggrepel)
library(treemap)
library(fmsb)
library(leaflet)
library(reshape)
```
### Open necessary datasets
```{r}
cwurData <- read.csv("cwurData.csv")
educationExpenditure <- read.csv("education_expenditure_supplementary_data.csv")
educationalAttainment <- read.csv("educational_attainment_supplementary_data.csv")
schoolCountry <- read.csv("school_and_country_table.csv")
shanghaiData <- read.csv("shanghaiData.csv")
timesData <- read.csv("timesData.csv")
```
### Getting basic information from tables {.tabset}

#### Central World University Rankings
```{r}
knitr::kable(head(cwurData,10), caption = "Central World University Rankings information (first 10 rows)")
```

#### Shanghai Rankings
```{r}
knitr::kable(head(shanghaiData,10),caption="Shanghai Ranking information (first 10 rows)")
```

#### Education attainment
```{r}
knitr::kable(head(educationalAttainment,10),caption="Education attainment information (first 10 rows)")
```

#### Education expenditure
```{r}
knitr::kable(head(educationExpenditure,10),caption="Education expenditure information (first 10 rows)")
```

#### Times Education Rankings
```{r}
knitr::kable(head(timesData,10),caption="Times Higher Education World University Rankings data information (first 10 rows)")
```

#### School & Country
```{r}
knitr::kable(head(schoolCountry,10),caption="School & country information (first 10 rows)")
```


### Review and reveal interesting facts
```{r}
glimpse(cwurData)
```

```{r}
cwurData %>% group_by(year) %>% 
  select(year,institution,world_rank) %>% top_n(-5, wt = world_rank) -> cwurTop5

plot_ly(cwurTop5, x = ~year) %>%
  add_trace(y = cwurTop5$world_rank, name = cwurTop5$institution, showlegend=TRUE, type = 'scatter', mode = 'lines+markers', color= cwurTop5$institution) %>%
  layout(title="World Ranked Universities by CWUR (2012-2015)",
         xaxis = list(showticklabels = TRUE, tickangle = 0, tickfont = list(size = 8)),
         yaxis = list(title = "World rank"),
         hovermode = 'compare')
```

```{r}
cwurPlotYear <- function(nYear) {
  cwurData %>% filter(year==nYear) %>% top_n(10,-world_rank) %>% 
  ggplot(aes(x=reorder(institution,-world_rank), y=world_rank)) + geom_bar(stat="identity", aes(fill=reorder(institution,-world_rank)), colour="black") +
    theme_bw() + coord_flip() +  scale_fill_manual(values=c(rep("lightgreen",7), "#CD7F32", "grey", "gold")) + guides(fill=FALSE) +
    labs(x="Institution", y="World Rank", 
        title=paste("Rank in ",nYear), subtitle="(smaller value is better)")
}
```

```{r fig.width = 10, fig.height=10, warning=FALSE}
cwurPlotYear(2012) -> d1
cwurPlotYear(2013) -> d2
cwurPlotYear(2014) -> d3
cwurPlotYear(2015) -> d4
grid.arrange(d1,d2,d3,d4, ncol=2)
```

```{r fig.height=20, fig.width=20, message=FALSE, warning=FALSE}
cwurData %>% group_by(country) %>% summarise(n = length(publications)) %>% top_n(10,n) %>% ungroup() -> c
cwurData %>% filter(country %in% c$country) %>%
ggplot(aes(x=country, y=publications, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Rank by publication", 
      title="Rank by publication", subtitle="Grouped by country, smaller value is better") + theme(text = element_text(size = 20)) -> d1
cwurData %>% filter(country %in% c$country) %>%
ggplot(aes(x=country, y=citations, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Rank by citations", 
      title="Rank by citations", subtitle="Grouped by country, smaller value is better") + theme(text = element_text(size = 20)) -> d2
cwurData %>% filter(country %in% c$country) %>%
ggplot(aes(x=country, y=patents, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Rank by patents", 
      title="Rank by patents", subtitle="Grouped by country, smaller value is better") + theme(text = element_text(size = 20)) -> d3
cwurData %>% filter(country %in% c$country) %>%
ggplot(aes(x=country, y=quality_of_education, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Rank by quality of education", 
      title="Rank by quality of education", subtitle="Grouped by country, smaller value is better") + theme(text = element_text(size = 20)) -> d4
cwurData %>% filter(country %in% c$country) %>%
ggplot(aes(x=country, y=alumni_employment, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Rank by alumni employment", 
      title="Rank by alumni employment", subtitle="Grouped by country, smaller value is better") + theme(text = element_text(size = 20)) -> d5
cwurData %>% filter(country %in% c$country) %>%
ggplot(aes(x=country, y=quality_of_faculty, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Rank by quality of faculty", 
      title="Rank by quality of faculty", subtitle="Grouped by country, smaller value is better") + theme(text = element_text(size = 20)) -> d6
grid.arrange(d1,d2,d3,d4,d5,d6, ncol=2)
```

```{r fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
cwurData %>% group_by(country,year) %>% 
  summarise(nr = length(world_rank), minw=min(world_rank), maxw=max(world_rank), avgw=round(mean(world_rank),0)) %>%
  select(country, year, nr, minw, maxw, avgw) %>% ungroup() -> ccwur
# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.5)
ccwur$hover <- with(ccwur, 
        paste("Country: ", country, '<br>', 
              "Year: ",year, "<br>",
              "Universities in top: ", nr, "<br>",
              "Min rank in top: ", minw, "<br>",
              "Max rank in top: ", maxw, "<br>",
              "Mean rank in top: ", avgw,"<br>"
              ))
g <- list(
  showframe = TRUE,
  showcoastlines = TRUE,
  projection = list(type = 'orthogonal')
)
plot_geo(ccwur, locationmode = 'country names') %>%
  add_trace(
    z = ~nr, color = ~nr, colors = 'Spectral', frame = ~year,
    text = ~hover, locations=~country, marker = list(line = l)
  ) %>%
  colorbar(title = 'Number of\nuniversities in top', tickprefix = '') %>%
  layout(
    title = with(ccwur, paste('Number of universities in top<br>Source:<a href="http://cwur.org/">Council of World University Ranking</a>')),
    geo = g
  )
```
## Check Shanghai Data
```{r}
shanghaiDataCld = shanghaiData
shanghaiDataCld$t_score = 
  0.1 * shanghaiDataCld$alumni + 0.2 * shanghaiDataCld$award + 0.2 * shanghaiDataCld$hici + 
  0.2 * shanghaiDataCld$ns + 0.2 * shanghaiDataCld$pub + 0.1 * shanghaiDataCld$pcp
shanghaiDataCld$total_score[is.na(shanghaiDataCld$total_score)] = shanghaiDataCld$t_score[is.na(shanghaiDataCld$total_score)]
```

```{r}
shanghaiDataCld = shanghaiDataCld[complete.cases(shanghaiDataCld),]
```

```{r message=FALSE, warning=FALSE}
#Fix the duplicate name for University of California-Berkeley
shanghaiDataCld$university_name[shanghaiDataCld$university_name=="University of California-Berkeley"] <- "University of California, Berkeley"
shanghaiDataCld %>% group_by(year) %>% 
  top_n(10, wt = total_score) %>% select(year,university_name,total_score,alumni, award, hici, ns, pub, pcp) %>% ungroup() -> top10univ
 
 #draw with plotly
 
plot_ly(top10univ, x = ~year) %>%
  add_trace(y = top10univ$total_score, name = top10univ$university_name, showlegend=TRUE, type = 'scatter', mode = 'lines+markers', color= top10univ$university_name) %>%
  layout(title="Shanghai (ARWU) World Ranks (2005-2015)<br>Best ranked universities based on total score", legend = list(orientation = 'h'),
         xaxis = list(showticklabels = TRUE, tickangle = 0, tickfont = list(size = 8)),
         yaxis = list(title = "Total score"),
         hovermode = 'compare')
```
### Shanghai Top Universities by Year
```{r}
top10SpiderWebYear <- function(nYear) {
    top10univ %>% filter(year==nYear) %>% ungroup() -> top10u
    top10 <- as.data.frame(cbind(top10u[,c(3,4,5,6,7,8,9)]))
    colnames(top10) <- c("Total Score", "Alumni with Nobel", "Awarded Nobel", "Highly Cited", 
                         "Nature&Science", "Publications", "PCAP")
    rownames(top10) <- top10u$university_name
    rmin <- apply(top10,2,min); rmax <- apply(top10,2,max)
     rmax <- 100
     rmin <- 0
    colors_border=c( "tomato", "blue", "gold", "green", "magenta", 
                 "yellow", "grey", "lightblue", "brown", "red", "lightgreen", "cyan" )
    par(mfrow=c(4,3))
    par(mar=c(1,1,5,1))
    for(i in 1:nrow(top10)){
      colorValue<-(col2rgb(as.character(colors_border[i]))%>% as.integer())/255
      radarchart(rbind(rmax,rmin,top10[i,]),
         axistype=2 , 
         pcol=rgb(colorValue[1],colorValue[2],colorValue[3], alpha = 1),
         pfcol=rgb(colorValue[1],colorValue[2],colorValue[3], alpha = 0.5),
         plwd=1 , plty=1,cglcol="grey", cglty=1, axislabcol="grey", cglwd=0.5,vlcex=0.7, 
         title=rownames(top10[i,]))
    }
    title(paste0('\nShanghai World University  Rankings top 10 (',nYear,')'),outer=TRUE,col.main='black',cex.main=1.5)
}
```
### Shanghai World University Rankings by Year {.tabset}
#### 2005
```{r fig.height=20, fig.width=20}
top10SpiderWebYear(2005)
```

#### 2006
```{r fig.height=20, fig.width=20}
top10SpiderWebYear(2006)
```

#### 2007
```{r fig.height=20, fig.width=20}
top10SpiderWebYear(2007)
```

#### 2008
```{r fig.height=20, fig.width=20}
top10SpiderWebYear(2008)
```

#### 2009
```{r fig.height=20, fig.width=20}
top10SpiderWebYear(2009)
```

#### 2010
```{r fig.height=20, fig.width=20}
top10SpiderWebYear(2010)
```

#### 2011
```{r fig.height=20, fig.width=20}
top10SpiderWebYear(2011)
```

#### 2012
```{r fig.height=20, fig.width=20}
top10SpiderWebYear(2012)
```

#### 2013
```{r fig.height=20, fig.width=20}
top10SpiderWebYear(2013)
```

#### 2014
```{r fig.height=20, fig.width=20}
top10SpiderWebYear(2014)
```

#### 2015
```{r fig.height=20, fig.width=20}
top10SpiderWebYear(2015)
```

## Rankings by All Countries
```{r fig.height=20, fig.width=20, message=FALSE, warning=FALSE}
merge(shanghaiDataCld,schoolCountry, by.x="university_name", by.y="school_name") -> scData

scData %>% group_by(country) %>% summarise(n = length(alumni)) %>% top_n(10,n) %>% ungroup() -> cs

scData %>% filter(country %in% cs$country) %>%
ggplot(aes(x=country, y=alumni, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Alumni with Nobel (score)", 
      title="Alumni with Nobel (score)", subtitle="Grouped by country") -> d1
scData %>% filter(country %in% cs$country) %>%
ggplot(aes(x=country, y=award, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Nobel awards score", 
      title="Nobel awards score", subtitle="Grouped by country") -> d2
scData %>% filter(country %in% cs$country) %>%
ggplot(aes(x=country, y=hici, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Highly cited score", 
      title="Highly cited score", subtitle="Grouped by country") -> d3
scData %>% filter(country %in% cs$country) %>%
ggplot(aes(x=country, y=ns, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Nature & Science publications score", 
      title="Nature & Science publications score", subtitle="Grouped by country") -> d4
scData %>% filter(country %in% cs$country) %>%
ggplot(aes(x=country, y=pub, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Publications score", 
      title="Publications score", subtitle="Grouped by country") -> d5
scData %>% filter(country %in% cs$country) %>%
ggplot(aes(x=country, y=pcp, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Per capita performance score", 
      title="Per capita performance score", subtitle="Grouped by country") -> d6

grid.arrange(d1,d2,d3, d4, d5, d6, ncol=2)
```

```{r fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
scData %>%  group_by(country, year) %>% 
summarise(nr = length(total_score), minw=min(total_score), maxw=max(total_score), avgw=round(mean(total_score),0)) %>%
select(country, year, nr, minw, maxw, avgw) %>% ungroup() -> swur
# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.5)
swur$hover <- with(swur, 
      paste("Country: ", country, '<br>', 
            "Year: ",year, "<br>",
            "Universities: ", nr, "<br>",
            "Min total score: ", minw, "<br>",
            "Max total score: ", maxw, "<br>",
            "Mean total score: ", avgw,"<br>"
            ))
# specify map projection/options
g <- list(
showframe = TRUE,
showcoastlines = TRUE,
projection = list(type = 'Mercator')
)
plot_geo(swur, locationmode = 'country names') %>%
add_trace(
  z = ~nr, color = ~nr, colors = 'Spectral', frame = ~year,
  text = ~hover, locations=~country, marker = list(line = l)
) %>%
colorbar(title = 'Number of\nuniversities', tickprefix = '') %>%
layout(
  title = with(swur, paste('Number of universities<br>Source:<a href="http://www.shanghairanking.com">Shanghai Academic World University Rankings</a>')),
  geo = g
)
```
## Times Higher Education University Rankings
```{r}
#replace first the missing values (`-`) with NA
timesData$teaching[timesData$teaching=='-'] <- NA
timesData$international[timesData$international=='-'] <- NA
timesData$research[timesData$research=='-'] <- NA
timesData$citations[timesData$citations=='-'] <- NA
timesData$income[timesData$income=='-'] <- NA
timesData$total_score[timesData$total_score=='-'] <- NA

#replace factors with numeric
timesData$teaching <- as.numeric(as.character(timesData$teaching))
timesData$international <- as.numeric(as.character(timesData$international))
timesData$research <- as.numeric(as.character(timesData$research))
timesData$citations <- as.numeric(as.character(timesData$citations))
timesData$income <- as.numeric(as.character(timesData$income))
timesData$total_score <- as.numeric(as.character(timesData$total_score))

# replace NAs with 0
timesData$income[is.na(timesData$income)] <- 0
timesData$international[is.na(timesData$international)] <- 0

#calculate the total score
timesData$t_score = 
  0.3 * as.numeric(as.character(timesData$teaching)) + 
  0.075 * as.numeric(as.character(timesData$international)) + 
  0.3 * as.numeric(as.character(timesData$research)) + 
  0.3 * as.numeric(as.character(timesData$citations)) + 
  0.025 * as.numeric(as.character(timesData$income))
  
#replace the total_score where missing with the calculated value
timesData$total_score[is.na(timesData$total_score)] <- timesData$t_score[is.na(timesData$total_score)]
timesData$wr = as.numeric(as.character(timesData$world_rank))
```

```{r}
thePlotYear <- function(nYear) {
  timesData %>% filter(year==nYear) %>% top_n(10,-wr) %>% 
  ggplot(aes(x=reorder(university_name,-wr), y=wr)) + geom_bar(stat="identity", aes(fill=reorder(university_name,-wr)), colour="black") +
    theme_bw() + coord_flip() +  scale_fill_manual(values=c(rep("lightgreen",7), "#CD7F32", "grey", "gold")) + guides(fill=FALSE) +
    labs(x="University name", y="World Rank", 
        title=paste("Rank in ",nYear), subtitle="(smaller value is better)") 
}
```


```{r fig.height=20, fig.width=20, message=FALSE, warning=FALSE}
thePlotYear(2011) -> d1
thePlotYear(2012) -> d2
thePlotYear(2013) -> d3
thePlotYear(2014) -> d4
thePlotYear(2015) -> d5
thePlotYear(2016) -> d6
grid.arrange(d1,d2,d3,d4,d5,d6, ncol=2)
```

### Ranks by Year {.tabset}
```{r}
timesData %>% group_by(year) %>% 
  top_n(10, wt = total_score) %>% 
  select(year,university_name,total_score,teaching, international, research, citations, income) %>% ungroup() -> top10univ
theTop10SpiderWebYear <- function(nYear) {
    top10univ %>% filter(year==nYear) %>% ungroup() -> top10u
    top10 <- as.data.frame(cbind(top10u[,c(3,4,5,6,7,8)]))
    colnames(top10) <- c("Total Score", "Teaching", "International Outlook", "Research", 
                          "Citations","Industry Income")
    rownames(top10) <- top10u$university_name
    
    rmin <- apply(top10,2,min); rmax <- apply(top10,2,max)
     rmax <- 100
     rmin <- 0
  
    colors_border=c( "tomato", "blue", "gold", "green", "magenta", 
                 "yellow", "grey", "lightblue", "brown", "red", "lightgreen", "cyan" )

    par(mfrow=c(4,3))
    par(mar=c(1,1,5,1))
    for(i in 1:nrow(top10)){
      colorValue<-(col2rgb(as.character(colors_border[i]))%>% as.integer())/255
      radarchart(rbind(rmax,rmin,top10[i,]),
         axistype=2 , 
         pcol=rgb(colorValue[1],colorValue[2],colorValue[3], alpha = 1),
         pfcol=rgb(colorValue[1],colorValue[2],colorValue[3], alpha = 0.5),
         plwd=1 , plty=1,cglcol="grey", cglty=1, axislabcol="grey", cglwd=0.5,vlcex=0.7, 
         title=rownames(top10[i,]))
    }
    title(paste0('\nTimes Higher Education  World University Rankings top 10 (',nYear,')'),outer=TRUE,col.main='black',cex.main=1.5)
}
```

#### 2011
```{r fig.height=20, fig.width=20}
theTop10SpiderWebYear(2011)
```

#### 2012
```{r fig.height=20, fig.width=20}
theTop10SpiderWebYear(2012)
```

#### 2013
```{r fig.height=20, fig.width=20}
theTop10SpiderWebYear(2013)
```

#### 2014
```{r fig.height=20, fig.width=20}
theTop10SpiderWebYear(2014)
```

#### 2015
```{r fig.height=20, fig.width=20}
theTop10SpiderWebYear(2015)
```

#### 2016
```{r fig.height=20, fig.width=20}
theTop10SpiderWebYear(2016)
```

### All countries total scores and counts
```{r fig.height=20, fig.width=20, message=FALSE, warning=FALSE}
timesData %>% group_by(country) %>% summarise(n = length(teaching)) %>% top_n(10,n) %>% ungroup() -> ct
timesData %>% filter(country %in% ct$country) %>%
ggplot(aes(x=country, y=teaching, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Teaching score", 
      title="Teaching score", subtitle="Grouped by country") -> d1
timesData %>% filter(country %in% ct$country) %>%
ggplot(aes(x=country, y=international, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="International outlook score", 
      title="International outlook score", subtitle="Grouped by country") -> d2
timesData %>% filter(country %in% ct$country) %>%
ggplot(aes(x=country, y=research, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Research score", 
      title="Research score", subtitle="Grouped by country") -> d3
timesData %>% filter(country %in% ct$country) %>%
ggplot(aes(x=country, y=citations, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Citations score", 
      title="Citations score", subtitle="Grouped by country") -> d4
timesData %>% filter(country %in% ct$country) %>%
ggplot(aes(x=country, y=income, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Industry income score", 
      title="Industry income score", subtitle="Grouped by country") -> d5
timesData %>% filter(country %in% ct$country) %>%
ggplot(aes(x=country, y=total_score, col=country)) + guides(col=FALSE) +
  geom_boxplot() +  theme_bw() + coord_flip() + 
  labs(x="Country", y="Total score", 
      title="Total score", subtitle="Grouped by country") -> d6
grid.arrange(d1,d2,d3,d4, d5, d6, ncol=2)
```

```{r message=FALSE, warning=FALSE}
timesData$total_score = as.numeric(as.character(timesData$total_score))
#replace with 0 the missing total_score values - this will affect the aggregated values

timesData %>% group_by(country,year) %>% 
summarise(nr = length(total_score), minw=min(total_score), maxw=max(total_score), avgw=round(mean(total_score),0)) %>%
select(country, year, nr, minw, maxw, avgw) %>% ungroup() -> ther

# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.5)

ther$hover <- with(ther, 
      paste("Country: ", country, '<br>', 
            "Year: ",year, "<br>",
            "Universities: ", nr, "<br>",
            "Min total score: ", minw, "<br>",
            "Max total score: ", maxw, "<br>",
            "Mean total score: ", avgw,"<br>"
            ))
# specify map projection/options
g <- list(
showframe = TRUE,
showcoastlines = TRUE,
projection = list(type = 'Mercator')
)
plot_geo(ther, locationmode = 'country names') %>%
add_trace(
  z = ~nr, color = ~nr, colors = 'Spectral', frame = ~year,
  text = ~hover, locations=~country, marker = list(line = l)
) %>%
colorbar(title = 'Number of\nuniversities', tickprefix = '') %>%
layout(
  title = with(ther, paste('Number of universities<br>Source:<a href="https://www.timeshighereducation.com/world-university-rankings">Times Higher Education World University Ranking</a>')),
  geo = g
)
```


